Sexual selection improves population fitness: a systematic review and meta-analysis

### 2019-03-08 Response_to_editorial_requests.Rmd

We are delighted to provide a revised manuscript for publication in \textit{Nature Communications}. Below we provide a point-by-point response to the editorial requests as well as a response to comments by Prof. Jacek Radwan.

## Editorial Requests

\begin{enumerate}
  \item \textit{Please supply the main manuscript file in Microsoft Word or LaTeX format. Please supply a Supplementary Information file in PDF format.} \\ 
  The main manuscript is provided in LaTeX format (.tex) and the Supplementary Information is now in pdf format. However, we retain the HTML formatting for the Supplementary Information hosted on \hyperlink{https://justincally.github.io/SexualSelection/}{Github}.

  \item \textit{Please edit the title so that it is 15 words or fewer and does not include punctuation} \\
  <!-- Sexual selection improves population fitness based on a systematic review and meta-analysis -->
  We have changed our title to: Meta-analytic evidence that sexual selection improves population fitness

@@

  \item \textit{The final paragraph of the Introduction should summarise the major results and conclusions of this manuscript, in the present tense.} \\
  <!-- We had previously included this in an earlier draft and cut it. Can add it back  -->

  \item \textit{Please shorten all subheadings in the Results section to fewer than 60 characters including spaces.} \\
  Sexual selection is associated with higher mean values for most fitness components \textbf{to} Sexual selection improves average fitness for most traits. \\
  Sexual selection reduces phenotypic variance, for female traits in stressful environments \textbf{to} Effects of sexual selection on phenotypic variance

@@

  \item \textit{Please do not use italics or bold font to convey emphasis (in both the main text and the display items).} \\
  Is this the latin? (e.g. /Prima facie / Tabbles have bold, figures have bold...)

  \item \textit{Please avoid using speech marks around words or phrases. In most cases they are unnecessary.} \\
  Speech marks around the following words/phrases have now been removed: population fitness (l.21), purged (l.175), softer (l.199), harder (l.199), 'good genes' (l.243), attractive (l.244), unambiguous (l.359).

  Single quotes for technical terms

@@

  All headings are under 60 characters in length, we have some additional Supp Methods in the Supp info but it is more or an appendage to the Supp tables and search terms (which would not nicely format in the main text)

  \item \textit{Please rename the Methods section as "Methods".} \\

  Done

  \item \textit{All Nature Communications manuscripts must include a section titled "Data Availability" as a separate section after the Methods section and before the References.}

### 2019-03-08 Manuscripts/Manuscript_MetaAnalysis.Rmd
organising repo

##Code and data availability

The code and data used to perform this meta-analysis is available as Electronic Supplementary Material and on Github (https://justincally.github.io/SexualSelection/). The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results. \phantomsection

>>>>

##Code availability

The code used to perform this meta-analysis is available on Github (https://justincally.github.io/SexualSelection/). The repository (https://github.com/JustinCally/SexualSelection) provides complete data tables of effect sizes, variance and sample sizes needed to reproduce our results. \phantomsection

##Data availability

All data are available on Github (https://github.com/JustinCally/SexualSelection).

### 2019-03-08 meta_analysis_sexual_selection_pop_fitness.Rmd
organising repo

```{r}
read.csv('data/Eligibility Workbook(22.02).csv', fileEncoding="UTF-8") %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

knitr::include_graphics(path = "figures/ForestPlot_size_reduced.png") 
```

@@

ggsave(plot = funnel.plot, filename = "figures/funnel_plot.eps", height = 7.5, width = 10)
funnel.plot
```
<br></br>
**Figure 3a:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001). The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision. Counter to expectations of publication bias these positive studies are not just 'low precision, large effect' results. Funnel plot asymmetry may also be due to genuine heterogeneity in effect sizes between studies, which is high in the present meta-analysis because it covers many species, outcome measurements, and experimental designs.

>>>>

```{r}
read.csv('data/Eligibility Workbook.csv', fileEncoding="UTF-8") %>%
  kable("html") %>% kable_styling() %>%
  scroll_box(width = "100%", height = "500px")
```
<br></br>

@@

knitr::include_graphics(path = "figures/ForestPlot_large.png") 
```

@@

#ggsave(plot = funnel.plot, filename = "figures/funnel_plot.eps", height = 7.5, width = 10)
funnel.plot
```
<br></br>
**Figure 3a:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 6.22, p < 0.0001). The asymmetry appears to come from a spread of positive effect sizes outside the funnel and of varying degrees of precision. Counter to expectations of publication bias these positive studies are not just 'low precision, large effect' results. Funnel plot asymmetry may also be due to genuine heterogeneity in effect sizes between studies, which is high in the present meta-analysis because it covers many species, outcome measurements, and experimental designs.
